# in this markdown, I will reduce the sample size by taking the mean of the house price by year

```{r}
library(dplyr)
```

```{r}
house <- read.csv("house_simplified.csv")
```

```{r}
house_reduced <- house %>% dplyr::select("year",
                                         "house_id",
                                         "resale_price")
```

```{r}
length(unique(house_reduced$house_id))
```

```{r}
house_reduced2 <- house_reduced[duplicated(house_reduced$house_id)|duplicated(house_reduced$house_id, fromLast = TRUE),]


```
# Calculating the mean price per house_id (based on address and floor)
```{r}

test <- aggregate(x = house_reduced$resale_price,
          by = list(house_reduced$house_id,house_reduced$year),
          FUN=mean)

test2 <- aggregate(x = house_reduced$resale_price,
          by = list(house_reduced$year,house_reduced$house_id),
          FUN=mean)


house_mean <- merge(house, test2, by.x = c("house_id", "year"), by.y = c("Group.2", "Group.1"))
names(house_mean)[names(house_mean) == "x"] <- "mean_price"

house_mean$identifier <- paste(house_mean$name,house_mean$year)
```

```{r}
write.csv(house_mean, file = "house_mean.csv")
```

```{r}
house_unique_year <- house_mean %>% distinct(house_mean$identifier,.keep_all = T)
length(unique(house_unique_year$identifier))
```
```{r}
write.csv(house_unique_year, file = "house_reduced.csv")
```

```{r}
house <- read.csv("house_mean.csv")
```

# Calculate price per square meter 
```{r}
house$price_per_m2 <- house$resale_price/house$floor_area_sqm
```

# total number of unique addresses
```{r}
length(unique(house$id))
```

# Calculate the mean price for each coordinate
```{r}
mean_price <- aggregate(x = house$price_per_m2,
          by = list(house$id,house$year),
          FUN=mean)

names(mean_price)[names(mean_price) == "x"] <- "mean_price_per_m2"
```

# merge back from original dataset
```{r}
house_mean_per_m2 <- merge(house, mean_price, by.x = c("id", "year"), by.y = c("Group.1", "Group.2"))
```

# add additional identifier for unique address and year
```{r}
house_mean_per_m2$add_year <- paste(house_mean_per_m2$add,house_mean_per_m2$year)
```

# total unique observations
```{r}
length(unique(house_mean_per_m2$add_year))
```
# filter unique addresses
```{r}
library(dplyr)
house_final <- house_mean_per_m2 %>% distinct(house_mean_per_m2$add_year,.keep_all = T)
```

# fix the year column
```{r}
house_final$year <- paste("20", house_final$year)
house_final$year <- gsub('\\s+', '', house_final$year)
```

# Export
```{r}
write.csv(house_final, file = "house.csv")
```


# load in data
```{r}
house <- read.csv("house.csv")
```

# keep unique addresses
```{r}
template <- house %>% distinct(house$add,.keep_all = F)
```

# iterate each row 8 times
```{r}
template2 <- as.data.frame(template[rep(seq_len(nrow(template)), each = 8), ])
```

```{r}
write.csv(template2, file = "templated.csv")
```

# Load in the template which is edited with excel
```{r}
template <- read.csv("template.csv")
template$add_year <- paste(template$add, template$year)
```

# create merging column
```{r}
house$add_year <- paste(house$add, house$year)
```

# merge back to create address with complete 2014 - 2021 with NA data
```{r}
house_complete <- right_join(house, template, by = c("add_year" = "add_year"))
```
# Export
```{r}
write.csv(house_complete, file = "house_complete.csv")
```


# Explore the final dataset 
```{r}
house <- read.csv("house_complete.csv")

NA_total <- sum(is.na(house$mean_price_per_m2))
NA_total/73800 * 100
# 24.06369% missing data
```






