# In this RMD, I performed: 1). Aggregated HDB resale flat datasets. 2). Data cleaning. 3). Geocoded HDB resale flat addresses into spatial coordinates

# HDB resale flat transaction data cleaning and geocoding
```{r}
library(dplyr)
library(tidyverse)
```


# Load in the 3 datasets for HDB resale flat price in Singapore from 2012 - 2021
```{r}
price4 <- read.csv("resale-flat-prices-based-on-registration-date-from-jan-2017-onwards.csv")
price3 <- read.csv("resale-flat-prices-based-on-registration-date-from-jan-2015-to-dec-2016.csv")
price2 <- read.csv("resale-flat-prices-based-on-registration-date-from-mar-2012-to-dec-2014.csv")
```


# Filter housing price in 2012, 2013 and 2014
```{r}
price2012 <- price2 %>% filter(month == "2012-03" | month == "2012-04" | month == "2012-05" | month == "2012-06" | month == "2012-07" | month == "2012-08" | month == "2012-09" 
                               | month == "2012-10" | month == "2012-11" | month == "2012-12")

price2013 <- price2 %>% filter(month == "2013-01" | month == "2013-02" | month == "2013-03" | month == "2013-04" | month == "2013-05" | month == "2013-06" | month == "2013-07" 
                               | month == "2013-08" | month == "2013-09" | month == "2013-10" | month == "2013-11" | month == "2013-12")
                            

price2014 <- price2 %>% filter(month == "2014-01" | month == "2014-02" | month == "2014-03" | month == "2014-04" | month == "2014-05" | month == "2014-06" | month == "2014-07" 
                               | month == "2014-08" | month == "2014-09" | month == "2014-10" | month == "2014-11" | month == "2014-12")
```

# Calucate remaining_lease for housing price in 2012, 2013 and 2014
```{r}
price2012$remaining_lease = (99 - (2012 - price2012$lease_commence_date))
price2013$remaining_lease = (99 - (2013 - price2013$lease_commence_date))
price2014$remaining_lease = (99 - (2014 - price2014$lease_commence_date))
price2_final <- rbind(price2012, price2013, price2014)
```


# Combine housing price from 2012-2021 into a single data frame
```{r}
housing_price <- rbind(price4, price3)
housing_price_final <- rbind(housing_price, price2_final)

# Add column for full address, this is for the purpose of geocoding later on
housing_price_final$add <- paste("Block", housing_price_final$block, housing_price_final$street_name, "Singapore")
housing_price_final$name <- paste("Block", housing_price_final$block, housing_price_final$street_name, "Singapore", housing_price_final$storey_range, housing_price_final$floor_area_sqm)
data <- arrange(housing_price_final, month)

```

# Convert date into date format
```{r}
data$month <- as.Date(paste0(as.character(data$month), "-01"))
```

# Convert categorical variables as factors
```{r}
data$storey_range <- factor(data$storey_range)
data$flat_model <- factor(data$flat_model)
data$flat_type <- factor(data$flat_type)
```

# filter out housing data before 2014 March, this is due to the policy change to HDB housing valuation in March 2014
```{r}
data <- data[data$month >= as.Date("2014-03-01"), ]
```

# Data Exploration: Flat_models
```{r}
flat_models <- data.frame(
  "flat_model" = names(table(data$flat_model)),
  "total" = as.numeric(table(data$flat_model)),
  check.names = FALSE
)

flat_models <- flat_models[order(flat_models$total, decreasing = TRUE), ]
rownames(flat_models) <- NULL
kable(flat_models)
```

# Flat model categorization
```{r}
data$flat_model_cate <- data$flat_model
data$flat_model_cate <- as.factor(data$flat_model_cate)

levels(data$flat_model_cate)

levels(data$flat_model_cate)[levels(data$flat_model_cate)%in%c("Simplified","Apartment","Standard","Maisonette","DBSS", "Model A2", "Type S1", "Model A-Maisonette", "Adjoined flat",
                                                               "Type S2", "Terrace", "Premium Apartment Loft", "Multi Generation", "Improved-Maisonette",
                                                               "Premium Maisonette", "2-room")] <- "Others"

flat_model_cate <- data.frame(
  "flat_model_cate" = names(table(data$flat_model_cate)),
  "total" = as.numeric(table(data$flat_model_cate)),
  check.names = FALSE
)

flat_model_cate <- flat_model_cate[order(flat_model_cate$total, decreasing = TRUE), ]
rownames(flat_model_cate) <- NULL
kable(flat_model_cate)

```


# Data Exploration: flat_types
```{r}
flat_types <- data.frame(
  "flat_type" = names(table(data$flat_type)),
  "total" = as.numeric(table(data$flat_type))
)
kable(flat_types)
```

# Categorise flat_model into fewer categories 
```{r}
data$flat_type_cate <- data$flat_type
data$flat_type_cate <- as.factor(data$flat_type_cate)

levels(data$flat_type_cate)

levels(data$flat_type_cate)[levels(data$flat_type_cate)%in%c("1 ROOM","2 ROOM")] <- "1-2 ROOM"
levels(data$flat_type_cate)[levels(data$flat_type_cate)%in%c("EXECUTIVE","MULTI-GENERATION")] <- "OTHERS"

flat_types_cate <- data.frame(
  "flat_type_cate" = names(table(data$flat_type_cate)),
  "total" = as.numeric(table(data$flat_type_cate))
)
kable(flat_types_cate)
```

# Add group ID
```{r}
data2 <- data

data2$ID <- seq.int(nrow(data2))
data2$add <- as.factor(data2$add)


cases <- data.frame(levels = levels(data2$add))

cases <- cases %>%
    mutate(id = rownames(cases))

data2 <- left_join(data2, cases, by = c("add" = "levels"))
```

# Geocoding HDB resale addresses to spatial coordinates data
```{r}
register_google(key = "") # Input google API
```

```{r}
all_add <- as.data.frame(unique(data2$add))
```

```{r}
all_latlon <- data.frame()
for (i in all_add){
  append_data <- data.frame(
    add = i,
    geocode(i, source = "google")
  )
  all_latlon <- rbind(all_latlon, append_data)
}

```

# export geocoded HDB resale flat data from March 2014 to October 2021
```{r}
write.csv(data3, file = "cleaned_data_final.csv")
```

# Save data
```{r}
save.image(file = "myprogress.RData")
```




