# In this Rmd, I performed haversine distance calculation for spatial proximity to 7 amenities: CBD, train stops, park, hospital, shopping malls, bus stops, and university


```{r}
library(geosphere)
```

# Load in data 
```{r}
house <- read.csv("cleaned_data_final.csv")
```

# convert remaining lease from character to integer 
```{r}
house$remaining_lease_final <- substr(house$remaining_lease, start = 1, stop = 2)
house$remaining_lease_final <- as.integer(house$remaining_lease_final)
```

# Convert to spatialpoints 
```{r}
house_sp <- SpatialPoints(coords = cbind(house$lon,house$lat), proj4string = CRS("+init=epsg:4326"))
```

# calculate distance to CBD
```{r}
cbd_dist <- as.data.frame(distm(x = house_sp, c(103.85255323664575,1.2786774240431218), fun = distHaversine)) #coordinate for CBD
house <- cbind(house, cbd_dist)
names(house)[names(house) == 'V1'] <- 'cbd_distance'
```

# Calculate distance to train stops
```{r}
train <- read_sf("lta-mrt-station-exit-kml.kml")
train_pp <- bus[,c("geometry")]
train_coord <- train_pp %>%
  mutate(lat = unlist(map(train_pp$geometry,1)),
         long = unlist(map(train_pp$geometry,2)))

train_sp <- SpatialPoints(coords = cbind(train_coord$lat,train_coord$long), proj4string = CRS("+init=epsg:4326"))

# Calculate distance matrix 
train_dist <- as.data.frame(distm(x = house_sp, train_sp, fun = distHaversine))

# Extract mininum distance to train station
min_train_distance <- as.data.frame(apply(train_dist, 1, FUN = min))

# join data
house <- cbind(house, min_train_distance)
names(house)[names(house) == "apply(train_dist, 1, FUN = min)"] <- 'train_distance'

```

# distance to park
```{r}
parks <- read_sf("RelaxSG.kml")
parks_pp <- parks[,c("geometry")]
parks_coord <- parks_pp %>%
  mutate(lat = unlist(map(parks_pp$geometry,1)),
         long = unlist(map(parks_pp$geometry,2)))

parks_sp <- SpatialPoints(coords = cbind(parks_coord$lat,parks_coord$long), proj4string = CRS("+init=epsg:4326"))

parks_dist <- as.data.frame(distm(x = house_sp, parks_sp, fun = distHaversine))

# Extract mininum distance to parks station
min_park_distance <- as.data.frame(apply(parks_dist, 1, FUN = min))

# join data
house <- cbind(house, min_park_distance)
names(house)[names(house) == "apply(parks_dist, 1, FUN = min)"] <- 'park_distance'

```

# Calculate distance to hospital
```{r}
hospital <- read_sf("hospital.kml")
hospital_sp <- SpatialPoints(coords = cbind(hospital$lon, hospital$lat), proj4string = CRS("+init=epsg:4326"))
hospital_dist <- as.data.frame(distm(x = house_sp, hospital_sp, fun = distHaversine))

# Extract mininum distance to parks station
min_hospital_distance <- as.data.frame(apply(hospital_dist, 1, FUN = min))

# join data
house <- cbind(house, min_hospital_distance)
names(house)[names(house) == "apply(hospital_dist, 1, FUN = min)"] <- 'hospital_distance'
```

# Calculate distance to university
```{r}
# first obtain unversity locations using open street map (OSM)
subzone <- read_sf("SUBZONE")
sg_outline <- subzone %>% st_union()
p_bbox <- st_bbox(st_transform(sg_outline, 4326))
sg_uni_osm <- opq(bbox = p_bbox) %>%
  add_osm_feature(key = "amenity", value = "university") %>% 
  osmdata_sf()
uni_pp <- sg_uni_osm$osm_points[,c("osm_id")] %>% st_transform(4326) %>% st_intersections(sg_outline)


# transform geometry into long and lat
uni_coord <- uni_pp %>%
  mutate(lat = unlist(map(uni_pp$geometry,2)),
         long = unlist(map(uni_pp$geometry,1)))

uni_sp <- SpatialPoints(coords = cbind(uni_coord$lon,uni_coord$lat), proj4string = CRS("+init=epsg:4326"))
uni_dist <- as.data.frame(distm(x = house_sp, uni_sp, fun = distHaversine))
min_uni_distance <- as.data.frame(apply(uni_dist, 1, FUN = min))
house <- cbind(house, min_uni_distance)
names(house)[names(house) == "apply(uni_dist, 1, FUN = min)"] <- 'uni_distance'
```

# Calculate distance to bus stops
```{r}
# read in bus stop shp
bus_pp <- read_sf("BusStopLocation_Jan2022")

# unlist geometry
bus_coord <- bus_pp %>%
  mutate(lat = unlist(map(bus_pp$geometry,1)),
         long = unlist(map(bus_pp$geometry,2)))

bus_df <- as.data.frame(bus_coord) %>%
  st_as_sf(coords = c("lat", "long"), crs = 3414) %>%
  st_transform(4326)

bus_df <- bus_df %>%
  mutate(lat = unlist(map(bus_df$geometry,1)),
         long = unlist(map(bus_df$geometry,2)))

bus_sp <- SpatialPoints(coords = cbind(bus_df$lat,bus_df$long), proj4string = CRS("+init=epsg:4326"))
plot(bus_sp)

# haversine distance to bus stops
bus_dist <- as.data.frame(distm(x = house_sp, bus_sp, fun = distHaversine))
min_bus_distance <- as.data.frame(apply(bus_dist, 1, FUN = min))
house <- cbind(house, min_bus_distance)
names(house)[names(house) == "apply(bus_dist, 1, FUN = min)"] <- 'bus_distance'
```
# Calculate distance to shopping malls
```{r}
mall <- read.csv("sg_malls.csv")
mall_sp <- SpatialPoints(coords = cbind(mall$lon,mall$lat), proj4string = CRS("+init=epsg:4326"))
mall_dist <- as.data.frame(distm(x = house_sp, mall_sp, fun = distHaversine))
min_mall_distance <- as.data.frame(apply(mall_dist, 1, FUN = min))
house <- cbind(house, min_mall_distance)
names(house)[names(house) == "apply(mall_dist, 1, FUN = min)"] <- 'mall_distance'
```

```{r}
write.csv(house, file = "ed_distance.csv")
```


# clean dataset
```{r}
house$year <- format(as.Date(house$month, format="%d/%m/%Y"),"%Y")
class(house$year)

house$year <- substr(house$year, 3, 4)
house$year <- as.numeric(house$year)
class(house$year)


house$name <- as.factor(house$name)
cases <- data.frame(levels = levels(house$name))
cases <- cases %>% 
  mutate(id = rownames(cases))

names(cases)[names(cases) == "id"] <- "house_id"
house <- left_join(house, cases, by = c("name" = "levels"))

write.csv(house, file = "house_final.csv")
```



